### 2017-01-04 robust-software.tex
Extending the note on version control and maintainability

Note: one practice \emph{not} included in the list below is the use of version control.
We think this is essential to building software,
and indeed to doing reproducible scientific work of any kind
\cite{wilson2014,wilson2016}.
However,
our focus in this short guide is on the software that is built,
not on the process used to build it.

>>>>

Note: one practice \emph{not} included in the list below is the use of version control.
We think this is essential to building software of any kind
\cite{wilson2014,wilson2016}.
However,
our focus in this short guide is on the software that is built,
not on the process used to build it.
Similarly,
we do not explicitly discuss code review,
unit testing,
and other practices essential to maintainability and sustainable software development.
